---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Alayna Garlitch"
date: "8/28/2019"
output: 
  html_document: 
    fig_height: 7
    fig_width: 10
    highlight: textmate
    theme: yeti
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

In the file, there are 1846 rows and 3 variables/columns.The 3 variables include x, y, and the name of the specified data set.

### Exercise 2

The correlation coefficient is -.0645.

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

The correlation coefficient for the star dataset is -0.0630.

Blah blah blah...

```{r plot-star}

```

I'm some text, you should replace me with more meaningful text...

```{r cor-star}

```

### Exercise 4

The correlation coefficient for the circle dataset is -0.0683.

```{r}

```

```{r}

```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)